This is the Title

### 2017-03-10 abc/paper/paper.tex
Make minimum displacement 0x20. Print out instruction bytes that aren't printable; in the current tests, the only remaining violations are INT 21 (expected, for tests) and the known bug in store16.
Fix store16 to be printable.
OK, twocolumn is working, so now what remains are to write the insertable bits and include them in the right place.

@@

 NEED TO FIX:
  - jump at least 0x20
  - store16 (not printable)
  - Not bug
  - some kind of output other than \_putc

@@

@@

>>>>

``interrupt is a way of telling the operating system: Check this out!''

@@

 NEED TO FIX:
  - some kind of output other than \_putc

 TOP PERFORMANCE IMPROVEMENTS:
  - don't jump at end of every block
  - don't assume a block needs to be split just because it's 0x7e-0x20.
    measure from the last jump!

@@

The CISC Ridiculous

@@

awesome text art headings?

Truly self-documenting
Giving new meaning to "program committee" "evaluating" my paper
For good reasons that I will explain later...

RISC ROLL
